The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-28 paper/ms.tex
Willott results

@@

\begin{figure*}
\epsscale{1.00}
\plotone{fig/OD1_w_dust_box_0.png} % pdf available
\caption{Parameter dispersion fitting the Willott with the Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{}
\end{figure*}

\begin{figure*}
\epsscale{1.00}
\plotone{fig/OD1_wo_dust_box_0.png} % pdf available
\caption{Parameter dispersion fitting the Willott with the No-Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{}
\end{figure*}

>>>>

\subsection{Willott}

We performed MCMC runnings with 100.000 steps over the 64 small 
cubic boxes (of $250$ \hMpc side length) fitting the LF to the 
Willott observational data, comparing the two cases; with and 
without dust attenuation. (figures \ref{fig:OD1_MCMC_best_steps_w} and 
\ref{fig:OD1_MCMC_best_steps_wo}). 
We used the Likelihood Ratio criterion ($\mathcal{LR}= 0.5$) to
define the $1\sigma$ confidence interval for our parameters.

$M_0$ is quite similar in booth cases (they are compatible within 
the error bars), the turnover point corresponds to the same mass.
$\gamma$ and $L_0$ shown a significative difference in booth cases.
$\beta$ is hard to constraint in booth cases. 
The parameer was limited to vary in the range form 0.0 to 1.6. 
$1\sigma$ region covers the whole range.

The UV luminosity model (eqn. \ref{eqn:luminosity}) that we have 
chosen can be divided in two regimes; high mass regime 
(with $M > M_0$) and low mass regime (with $M < M_0$).

The observational dataset from Willott are in the high mass regime 
with one point in the low mass regime. It makes makes hard to impose
restrictions over $\beta$, but the other three parameters can be
well defined.

We also compare the likelihood of the two cases on each individual 
small box. The Dust Attenuation model is more acurrate than the
No-Dust Attenuation model in most of the cases as is shown in the figure 
\ref{fig:OD1_chi2_comparison}.

To study cosmic variance effects, we compared the best fit parameters
of each box and its likelihood value. We found that cosmic variance
effects are less significative in best fit parameters than MCMC parameter
estimation itself.

@@

\begin{figure*}
\epsscale{1.00}
\plotone{fig/OD1_w_dust_box_0.png} % pdf available
\caption{Parameter dispersion fitting the Willott with the Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{fig:OD1_MCMC_best_steps_w}
\end{figure*}

\begin{figure*}
\epsscale{1.00}
\plotone{fig/OD1_wo_dust_box_0.png} % pdf available
\caption{Parameter dispersion fitting the Willott with the No-Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{fig:OD1_MCMC_best_steps_wo}
\end{figure*}
